Comparisons in three center

### 2021-04-15 scripts/43_comparisons_3.Rmd
update
very hard to concentrate but damn I am getting things done ..

```{r}
cur <- read_csv('../data/shotgun_pheno/final_comprehensive.csv') %>% 
  select(fid, center, cr_d100, toxicity, icans, crs) %>% 
  filter(center != 'I') %>% # manually update the label for the "not_assessed"
  mutate(cr_d100 = case_when(
    fid == '2460A' ~ 'no',
    fid == '2293A' ~ 'no',
    fid == '2563A' ~ 'no',
    TRUE ~ cr_d100
  ))

pheno <- cur %>% 
  gather('pheno', 'value', cr_d100:crs)

>>>>

```{r}
# UPDATE THIS TABLE BABY
cur <- read_csv('../data/shotgun_pheno/final_comprehensive.csv') %>% 
  select(fid, center, cr_d100, toxicity, icans, crs) %>% 
  filter(center != 'I') %>% # manually update the label for the "not_assessed"
  mutate(cr_d100 = case_when(
    fid == '2460A' ~ 'no',
    fid == '2293A' ~ 'no',
    fid == '2563A' ~ 'no',
    TRUE ~ cr_d100
  ))

# Removing the patients that the data we can't use
# upated 2021-4-12
now <- read_csv('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/MSK/samples/eligible_sampleslist_JS.csv') %>% 
  filter(eligible == 'yes' & shotgun == 'yes') %>% 
  pull(pt_id)

final <- read_csv('../data/shotgun_pheno/final_comprehensive.csv') %>% 
  filter(center != 'I') %>% 
  mutate(pt_id = as.numeric(pt_id)) %>% 
  mutate(pt_id = if_else(center == 'P', pt_id + 8000, pt_id)) %>% 
  filter(pt_id %in% now) # keep to the most updated list

final %>% write_csv('../data/shotgun_pheno/final_comprehensive_UPDATED.csv')

# the final simple list with most up to date pheno label
simple <- cur %>% 
  filter(fid %in% final$fid)

simple %>% write_csv('../data/shotgun_pheno/final_comprehensive_UPDATED_simple.csv')
```

```{r}
pheno <- cur %>% 
  gather('pheno', 'value', cr_d100:crs)
